---
title: "analysis"
author: "Joyce Lee"
date: "03/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(lubridate)
library(tidyverse)
```

### Data wrangling

```{r}
driver_info <- read_csv("data/Driver_Info.csv")
incidents <- read_csv("data/Incidents.csv")
nswshifts <- read_csv("data/NSWshifts.csv") %>%
  distinct()
melbourneweather <- read_csv("data/melbourneweather_20150101_20210428.csv")
sydneyweather <- read_csv("data/sydneyweather_20150101_20210415.csv")
```

```{r}
incidents <- incidents %>%
  unite(EmployeeID, c("company", "EmployeeNumber"), remove = FALSE)
```

```{r}
nswshifts$VdsCompany <- toupper(nswshifts$VdsCompany)
nswshifts <- nswshifts %>%
  unite(EmployeeID, c("VdsCompany", "VdsEmployeeId"), remove = FALSE)


tmp <- incidents %>%
  filter(company == 'TDNSW') %>%
  select(ClaimNumber, EmployeeID,TypeOfClaimName,DateOccurred) %>%
  mutate(JoinDate = as.Date(DateOccurred)) %>%
  left_join(nswshifts %>%
              mutate(JoinDate = as.Date(VdsTripStartTime)),
            by = c("EmployeeID","JoinDate")) %>%
  mutate(match_type = case_when(
    is.na(VdsTripStartTime) ~ 0,
    DateOccurred >= VdsTripStartTime & DateOccurred <= VdsTripEndTime ~ 2,
    TRUE ~ 1
  ))
matched <-
  tmp %>%
  inner_join(
    tmp %>% group_by(ClaimNumber) %>% summarise(match_type = max(match_type)),
    by = c("ClaimNumber", "match_type")
  ) %>%
  arrange(match_type,ClaimNumber,VdsTripStartTime)

tmp2 <- incidents %>%
  filter(company == 'TDNSW') %>%
  select(ClaimNumber, EmployeeID,TypeOfClaimName,DateOccurred) %>%
  mutate(JoinDate = as.Date(DateOccurred)) %>%
  left_join(nswshifts %>%
              mutate(JoinDate = as.Date(VdsTripStartTime)) %>%
              group_by(EmployeeID, JoinDate) %>%
              summarise(shift_start = min(VdsTripStartTime)-30*60,
                        shift_end = max(VdsTripEndTime)+30*60),
            by = c("EmployeeID","JoinDate")) %>%
  mutate(match_type = case_when(
    is.na(shift_start) ~ 0,
    DateOccurred >= shift_start & DateOccurred <= shift_end ~ 2,
    TRUE ~ 1
  ))
matched <-
  tmp2 %>%
  inner_join(
    tmp2 %>% group_by(ClaimNumber) %>% summarise(match_type = max(match_type)),
    by = c("ClaimNumber", "match_type")
  ) %>%
  arrange(match_type,ClaimNumber,shift_start)
```

```{r}
melbourneweather <- melbourneweather %>%
  slice(-1:-9) %>%
  select(location, Melbourne, Melbourne_1) %>%
  rename(c(timestamp = location, `Melbourne Temperature` = Melbourne, `Melbourne Precipitation Total` = Melbourne_1)) 
melbourneweather <- melbourneweather %>%
        mutate(timestamp = ymd_hm(timestamp))

```

```{r}
sydneyweather <- sydneyweather %>%
  slice(-1:-9) %>%
  select(location, Sydney, Sydney_1) %>%
  rename(c(timestamp = location, `Sydney Temperature` = Sydney, `Sydney Precipitation Total` = Sydney_1)) 
sydneyweather <- sydneyweather %>%
        mutate(timestamp = ymd_hm(timestamp))
```

### Questions:
1. How are drivers' characteristics (Depot, gender, employee start date and age) affecting the incidents? Which is contributing the most incidents?
2. On what day have most incidents been found? Which hours are the peak and trough?
3. Has daytime or night been a significant cause of incidents?
4. What kind of weather (temperature and precipitation) is considered safer or dangerous for bus drivers?
5. Is there a relationship between drivers' driving hours within a day and the likelihood of getting into an incident?