---
title: "ETC5543 Business analytics creative activity"
subtitle: "Presentation"
author: "Joyce Lee"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: 
      - default
      - default-fonts
      - duke-blue
      - hygge-duke
      - libs/cc-fonts.css
      - libs/figure-captions.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r include=FALSE}
library(base)
library(broom)
library(caret)
library(citation)
library(ggridges)
library(hrbrthemes)
library(kableExtra)
library(lubridate)
library(parsnip)
library(plotly)
library(randomForest)
library(randomForestExplainer)
library(rsample)
library(rstatix)
library(tidyverse)
```

```{r include=FALSE}
driver_info <- read_csv("data/Driver_Info.csv") %>%
  filter(!Depot == "Not Given")
incidents <- read_csv("data/Incidents.csv")
nswshifts <- read_csv("data/NSWshifts.csv") %>%
  distinct()
melbourneweather <- read_csv("data/melbourneweather_20150101_20210428.csv")
sydneyweather <- read_csv("data/sydneyweather_20150101_20210415.csv")
```

```{r include=FALSE}
incidents <- incidents %>%
  unite(EmployeeID, c("company", "EmployeeNumber"), remove = FALSE)
```

```{r include=FALSE}
nswshifts$VdsCompany <- toupper(nswshifts$VdsCompany)
nswshifts <- nswshifts %>%
  unite(EmployeeID, c("VdsCompany", "VdsEmployeeId"), remove = FALSE)


tmp <- incidents %>%
  filter(company == 'TDNSW') %>%
  select(ClaimNumber, EmployeeID, ClaimCategoryName, TypeOfClaimName, DateOccurred) %>%
  mutate(JoinDate = as.Date(DateOccurred)) %>%
  left_join(nswshifts %>%
              mutate(JoinDate = as.Date(VdsTripStartTime)),
            by = c("EmployeeID","JoinDate")) %>%
  mutate(match_type = case_when(
    is.na(VdsTripStartTime) ~ 0,
    DateOccurred >= VdsTripStartTime & DateOccurred <= VdsTripEndTime ~ 2,
    TRUE ~ 1
  ))
matched <-
  tmp %>%
  inner_join(
    tmp %>% group_by(ClaimNumber) %>% summarise(match_type = max(match_type)),
    by = c("ClaimNumber", "match_type")
  ) %>%
  arrange(match_type,ClaimNumber,VdsTripStartTime)

tmp2 <- incidents %>%
  filter(company == 'TDNSW') %>%
  select(ClaimNumber, EmployeeID, ClaimCategoryName, TypeOfClaimName,DateOccurred) %>%
  mutate(JoinDate = as.Date(DateOccurred)) %>%
  left_join(nswshifts %>%
              mutate(JoinDate = as.Date(VdsTripStartTime)) %>%
              group_by(EmployeeID, JoinDate) %>%
              summarise(shift_start = min(VdsTripStartTime)-30*60,
                        shift_end = max(VdsTripEndTime)+30*60),
            by = c("EmployeeID","JoinDate")) %>%
  mutate(match_type = case_when(
    is.na(shift_start) ~ 0,
    DateOccurred >= shift_start & DateOccurred <= shift_end ~ 2,
    TRUE ~ 1
  ))
matched <-
  tmp2 %>%
  inner_join(
    tmp2 %>% group_by(ClaimNumber) %>% summarise(match_type = max(match_type)),
    by = c("ClaimNumber", "match_type")
  ) %>%
  arrange(match_type,ClaimNumber,shift_start)

tmp <- tmp %>%
  mutate(day_of_week = weekdays(as.Date(DateOccurred)))

tmp2 <- tmp2 %>%
  mutate(day_of_week = weekdays(as.Date(DateOccurred)))
```

```{r include=FALSE}
melbourneweather <- melbourneweather %>%
  slice(-1:-9) %>%
  select(location, Melbourne, Melbourne_1) %>%
  rename(c(timestamp = location, `Melbourne Temperature` = Melbourne, `Melbourne Precipitation Total` = Melbourne_1)) 
melbourneweather <- melbourneweather %>%
        mutate(timestamp = ymd_hm(timestamp))

```

```{r include=FALSE}
sydneyweather <- sydneyweather %>%
  slice(-1:-9) %>%
  select(location, Sydney, Sydney_1) %>%
  rename(c(timestamp = location, `Sydney Temperature` = Sydney, `Sydney Precipitation Total` = Sydney_1)) 
sydneyweather <- sydneyweather %>%
        mutate(timestamp = ymd_hm(timestamp))
```

class: center, middle

.pull-left[

## Organisation

<img src = "https://www.lynxx.com.au/wp-content/uploads/2015/12/Lynxx_logo-website2x.png" width = "50%" />

.blue["Translate" gathered data in to readable information]

.blue[Analyse information with insights]

.blue[Conclude the outcomes with potential solutions]

]

.pull-right[

## Client

<img src = "https://www.transdevmelbourne.com.au/media/10481/transdev-logo-new.png" width = "50%" />

.blue[Statistical links between accidents and factors]

.blue[Meaningful and logical patterns from the data]

.blue[Traffic congestion examination]

.blue[Variables of interest: Weather, Daylight vs Dark, Shift length, where incident occurred in shift, etc.]

]

**My goals**: 

To reveal the current conditions and existing problems of incidents, regarding variables of interest. 

To look at the associations precisely, using statistical approaches.


---
class: middle

# Data

* Driver_Info: All drivers' personal information with their employment records.

* Incidents: Incidents / claims made across NSW, VIC and WA with details recorded.

* NSWshifts: Shifts information in NSW, e.g. the start and end datetimes for the trips.   

* melbourneweather_20150101_20210428: Meteorological-relevant information (temperature, precipitation, humidity, etc.) measured hourly in Melbourne from 1st January, 2015 to 28th April, 2021.

* sydneyweather_20150101_20210415: Meteorological-relevant information (temperature, precipitation, humidity, etc.) measured hourly in Sydney from 1st January, 2015 to 15th April, 2021.


---

class: middle, center

.full-width[.content-box-duke-green[1) How are drivers' characteristics (Depot, gender and age) affecting the incidents? Do they genuinely contribute to the occurrence of incidents?]]

---

## Drivers had claims by **depot** (%) 

```{r echo=FALSE, message=FALSE, fig.dim=c(12,8)}
# all drivers in each depot
drvr_inc_dpt <- incidents %>%
  drop_na(EmployeeNumber) %>%
  distinct(EmployeeID, ClaimCategoryId, DateOccurred, .keep_all = TRUE) %>%
  right_join(driver_info, by = "EmployeeID") %>%
  mutate(driver_incident = case_when(is.na(ClaimNumber) ~ "No",
                                         !is.na(ClaimNumber) ~ "Yes")) %>%
  group_by(Depot, CompanyID, driver_incident, EmployeeID) %>%
  summarise(driver_depot = n_distinct(EmployeeID)) %>%
  filter(driver_incident == "Yes") %>%
  group_by(Depot, CompanyID) %>%
  summarise(num_drv_inc = sum(driver_depot))

total_drvr_dpt <- driver_info %>%
  group_by(Depot, CompanyID) %>%
  summarise(num_of_drvr = n())

drvr_inc_dpt %>%
  left_join(total_drvr_dpt, by = c("Depot", "CompanyID")) %>%
  mutate(has_incident_dpt = (num_drv_inc/num_of_drvr)*100) %>%
  mutate(across(has_incident_dpt, round, 2)) %>%
  ggplot(aes(x = Depot, y = has_incident_dpt, fill = CompanyID)) +
  geom_bar(stat = "identity") + 
  geom_text(aes(label = has_incident_dpt), vjust=1.6, color="white", size=2.5) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(y = "Drivers had claims", fill = "Company", title = "Proportion of drivers had claims by Depot")


```

---

## Drivers had claims by **depot** (%), classified with incidents severity

```{r echo=FALSE, message=FALSE}
severity_inc <- incidents %>%
  mutate(severity = case_when(TypeOfClaimName %in% c("MVA - Hit by Third Party", "MVA - Hit parked vehicle", "Customer Injury- Heavy Braking", "MVA - Hit moving vehicle while driving straight", "MVA - Hit moving vehicle while turning", "MVA - Hit stationary vehicle while turning", "MVA - Hit stationary vehicle driving straight", "MVA - Hit illegally parked vehicle", "MVA - Hit moving vehicle while changing lanes", "Pedestrian Injury - Hit by Transdev vehicle", "MVA - Hit bus station", "Employee Injury - Motor Vehicle Accident", "Motor Vehicle Collision", "Collision with Public") ~ "serious",
                              TypeOfClaimName %in% c("MVA - Hit tree/ tree branch", "MVA - Hit barrier/ bollard", "MVA - Near Miss", "MVA - Reversing", "MVA bus stop sign", "MVA bus stop pole") ~ "slight")) %>%
  filter(severity %in% c("serious", "slight"))

inc_severity_dept <- severity_inc %>%
  drop_na(EmployeeNumber) %>%
  distinct(EmployeeID, ClaimCategoryId, DateOccurred, .keep_all = TRUE) %>%
  right_join(driver_info, by = "EmployeeID") %>%
  mutate(driver_incident = case_when(is.na(ClaimNumber) ~ "No",
                                         !is.na(ClaimNumber) ~ "Yes")) %>%
  group_by(Depot, CompanyID, driver_incident, EmployeeID, severity) %>%
  summarise(driver_depot = n_distinct(EmployeeID)) %>%
  filter(driver_incident == "Yes") %>%
  group_by(Depot, severity, CompanyID) %>%
  summarise(num_drv_inc = sum(driver_depot))
  
total_drvr_dpt <- driver_info %>%
  group_by(Depot, CompanyID) %>%
  summarise(num_of_drvr = n())

svr_dpt <- inc_severity_dept %>%
  left_join(total_drvr_dpt, by = c("Depot", "CompanyID")) %>%
  mutate(has_incident_dpt = (num_drv_inc/num_of_drvr)*100) %>%
  mutate(across(has_incident_dpt, round, 2)) %>%
  pivot_wider(names_from = severity, values_from = has_incident_dpt) %>%
  mutate(serious = replace_na(serious, 0),
         slight = replace_na(slight, 0))

p1 <- svr_dpt %>%
  mutate(serious_label = paste0(CompanyID," - Serious"),
         slight_label = paste0(CompanyID," - Slight")) %>%
  plot_ly(x = ~Depot, color = ~CompanyID) %>%
  add_trace(y = ~serious, name = ~serious_label, type='bar',width = 0.3) %>%
  add_trace(y = ~slight, name = ~slight_label, type='bar', width=0.3,opacity=0.5) %>%
  layout(
    title = "Proportion of drivers had claims by Depot and Severity",
    yaxis = list(title = "Drivers had claims (%)",
                 range=c(0,100)),
    updatemenus = list(
      list(
        type = "buttons",
        #label = 'Category',
        buttons = list(
          list(method = "restyle",
               args = list('visible', c(rep(TRUE,3), rep(FALSE,3))),
               label = "Serious Only"),
          list(method = "restyle",
               args = list('visible', c(rep(FALSE,3), rep(TRUE,3))),
               label = "Slight Only"),
          list(method = "restyle",
               args = list('visible', TRUE),
               label = "Show All")
        )
      )
    )
  )

htmlwidgets::saveWidget(p1,paste0("p1.html"))
```

<iframe src="p1.html" width="90%" height="380" id="igraph" scrolling="no" seamless="seamless" frameBorder="0"> </iframe>

---

## Drivers had claims by **gender** (%), classified by company 

```{r echo=FALSE, message=FALSE, fig.dim=c(12,8)}
drvr_inc_gdr <- incidents %>%
  drop_na(EmployeeNumber) %>%
  distinct(EmployeeID, ClaimCategoryId, DateOccurred, .keep_all = TRUE) %>%
  right_join(driver_info, by = "EmployeeID") %>%
  mutate(driver_incident = case_when(is.na(ClaimNumber) ~ "No",
                                         !is.na(ClaimNumber) ~ "Yes")) %>%
  group_by(Gender, CompanyID, driver_incident, EmployeeID) %>%
  summarise(driver_gdr = n_distinct(EmployeeID)) %>%
  filter(driver_incident == "Yes") %>%
  group_by(Gender, CompanyID) %>%
  summarise(num_drv_inc = sum(driver_gdr))

total_drvr_gdr <- driver_info %>%
  group_by(Gender, CompanyID) %>%
  summarise(num_of_drvr = n())

drvr_inc_gdr %>%
  full_join(total_drvr_gdr, by = c("Gender", "CompanyID")) %>%
  mutate(num_drv_inc = replace_na(num_drv_inc, 0)) %>%
  mutate(has_incident_gdr = (num_drv_inc/num_of_drvr)*100) %>%
  mutate(across(has_incident_gdr, round, 2)) %>%
  ggplot(aes(x = Gender, y = has_incident_gdr, fill = Gender)) +
  geom_bar(stat = "identity") + 
  geom_text(aes(label = has_incident_gdr), vjust=1.6, color="white", size=2.5) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  theme_minimal() +
  facet_grid(.~CompanyID) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(y = "Drivers had claims", fill = "Gender", title = "Proportion of drivers had claims by Gender and company")
  
```

---

## Drivers had claims by **gender** (%), classified with incidents severity

```{r echo=FALSE, message=FALSE}
inc_severity_gdr <- severity_inc %>%
  drop_na(EmployeeNumber) %>%
  distinct(EmployeeID, ClaimCategoryId, DateOccurred, .keep_all = TRUE) %>%
  right_join(driver_info, by = "EmployeeID") %>%
  mutate(driver_incident = case_when(is.na(ClaimNumber) ~ "No",
                                         !is.na(ClaimNumber) ~ "Yes")) %>%
  group_by(Gender, CompanyID, driver_incident, EmployeeID, severity) %>%
  summarise(driver_depot = n_distinct(EmployeeID)) %>%
  filter(driver_incident == "Yes") %>%
  group_by(Gender, severity, CompanyID) %>%
  summarise(num_drv_inc = sum(driver_depot))
  
total_drvr_gdr <- driver_info %>%
  group_by(Gender, CompanyID) %>%
  summarise(num_of_drvr = n())

svr_gdr <- inc_severity_gdr %>%
  left_join(total_drvr_gdr, by = c("Gender", "CompanyID")) %>%
  mutate(has_incident_gdr = (num_drv_inc/num_of_drvr)*100) %>%
  mutate(across(has_incident_gdr, round, 2)) %>%
  pivot_wider(names_from = severity, values_from = has_incident_gdr) %>%
  mutate(serious = replace_na(serious, 0),
         slight = replace_na(slight, 0))

p2 <- svr_gdr %>%
  mutate(serious_label = paste0(CompanyID," - Serious"),
         slight_label = paste0(CompanyID," - Slight")) %>%
  plot_ly(x = ~Gender, color = ~CompanyID) %>%
  add_trace(y = ~serious, name = ~serious_label, type='bar') %>%
  add_trace(y = ~slight, name = ~slight_label, type='bar',opacity=0.5)  %>%
  layout(
    yaxis = list(title = "Drivers had claims (%)",
      range=c(0,100)
    ),
    title = "Proportion of drivers had claims by Gender and Severity",
    updatemenus = list(
      list(
        type = "buttons",
        label = 'Category',
        buttons = list(
          list(method = "restyle",
               args = list('visible', c(rep(TRUE,3), rep(FALSE,3))),
               label = "Serious Only"),
          list(method = "restyle",
               args = list('visible', c(rep(FALSE,3), rep(TRUE,3))),
               label = "Slight Only"),
          list(method = "restyle",
               args = list('visible', TRUE),
               label = "Show All")
        )
      )
    )
  )

htmlwidgets::saveWidget(p2,paste0("p2.html"))
```

<iframe src="p2.html" width="90%" height="380" id="igraph" scrolling="no" seamless="seamless" frameBorder="0"> </iframe>

---

## Gender vs MVA Incident T-test


```{css, echo=F}
    /* Table width = 100% max-width */

    .remark-slide table{
        width: 100%;
    }

    /* Change the background color to white for shaded rows (even rows) */

    .remark-slide thead, .remark-slide tr:nth-child(2n) {
        background-color: white;
    }
```

```{r echo=FALSE, message=FALSE}
gen_inc <- incidents %>%
  filter(str_starts(TypeOfClaimName, "MVA")) %>%
  drop_na(EmployeeNumber) %>%
  distinct(EmployeeID, ClaimCategoryId, DateOccurred, .keep_all = TRUE) %>%
  right_join(driver_info, by = "EmployeeID") %>%
  mutate(driver_incident = case_when(is.na(ClaimNumber) ~ "No",
                                         !is.na(ClaimNumber) ~ "Yes")) %>%
  group_by(Gender, driver_incident, EmployeeID) %>%
  summarise(driver_depot = n_distinct(EmployeeID)) %>%
  group_by(Gender, driver_incident) %>%
  summarise(num_drv_inc = sum(driver_depot))

tot_drv_gen <- driver_info %>%
  distinct(EmployeeID, Gender) %>%
  group_by(Gender) %>%
  summarise(num_of_drvr = n())

gen_inc_tab <- gen_inc %>%
  pivot_wider(names_from = driver_incident, values_from = num_drv_inc) %>%
  left_join(tot_drv_gen, by = "Gender") %>%
  mutate(has_incident_gdr = (Yes/num_of_drvr)*100) %>%
  mutate(across(has_incident_gdr, round, 2)) %>%
  rename(incident = Yes, `no incident` = No, total = num_of_drvr, prop = has_incident_gdr) 
gen_inc_tab %>%
  kable(caption = "Contingency table for gender and incident") %>%
  kable_styling()


```



```{r echo=FALSE}
test_x <- as.matrix(gen_inc_tab %>%
                      ungroup() %>%
                      select(incident, `no incident`))
CLTest_gen <- prop.test(test_x)
tidy(CLTest_gen) %>%
  kable() %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "scale_down") %>%
  scroll_box(width = "737px")
```

---

## Drivers had claims by **age** (%) 

```{r echo=FALSE, message=FALSE, fig.dim=c(12,8)}
inc_age <- incidents %>%
  drop_na(EmployeeNumber) %>%
  distinct(EmployeeID, ClaimCategoryId, DateOccurred, .keep_all = TRUE) %>%
  right_join(driver_info, by = "EmployeeID") %>%
  mutate(driver_age = today() - dmy(BirthDate),
         driver_age = driver_age/dyears(),
         driver_incident = case_when(is.na(ClaimNumber) ~ "No",
                                         !is.na(ClaimNumber) ~ "Yes"))
inc_age$driver_age <- round(inc_age$driver_age, digits = 0)
inc_age <- inc_age %>%
  mutate(age_group = case_when(driver_age >= 20 & driver_age <= 30 ~ "20-30",
                               driver_age >= 31 & driver_age <= 40 ~ "31-40",
                               driver_age >= 41 & driver_age <= 50 ~ "41-50",
                               driver_age >= 51 & driver_age <= 60 ~ "51-60",
                               driver_age >= 61 & driver_age <= 70 ~ "61-70",
                               driver_age >= 71 & driver_age <= 80 ~ "71-80",
                               driver_age >= 81 & driver_age <= 90 ~ "81-90"))
inc_age <- inc_age %>%
  group_by(age_group, driver_incident, EmployeeID) %>%
  summarise(driver_age_group = n_distinct(EmployeeID)) %>%
  filter(driver_incident == "Yes") %>%
  group_by(age_group) %>%
  summarise(num_drv_inc = sum(driver_age_group))


drvr_info_age <- driver_info %>%
  mutate(driver_age = today() - dmy(BirthDate),
         driver_age = driver_age/dyears())
drvr_info_age$driver_age <- round(drvr_info_age$driver_age, digits = 0)
drvr_info_age <- drvr_info_age %>%
  mutate(age_group = case_when(driver_age >= 20 & driver_age <= 30 ~ "20-30",
                               driver_age >= 31 & driver_age <= 40 ~ "31-40",
                               driver_age >= 41 & driver_age <= 50 ~ "41-50",
                               driver_age >= 51 & driver_age <= 60 ~ "51-60",
                               driver_age >= 61 & driver_age <= 70 ~ "61-70",
                               driver_age >= 71 & driver_age <= 80 ~ "71-80",
                               driver_age >= 81 & driver_age <= 90 ~ "81-90"))
drvr_info_age <- drvr_info_age %>%
  group_by(age_group) %>%
  summarise(num_of_drvr = n())

inc_age %>%
  full_join(drvr_info_age, by = "age_group") %>%
  mutate(has_incident_age = (num_drv_inc/num_of_drvr)*100) %>%
  mutate(across(has_incident_age, round, 2)) %>%
  ggplot(aes(x = age_group, y = has_incident_age, fill = age_group)) +
  geom_bar(stat = "identity") + 
  geom_text(aes(label = has_incident_age), vjust=1.6, color="white", size=2.5) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(x = "Age group", y = "Drivers had claims", fill = "Age group", title = "Proportion of drivers had claims by Age")
```

---
## Drivers had claims by **age** (%), classified with incidents severity

```{r echo=FALSE, message=FALSE, warning=FALSE}
inc_severity_age <- severity_inc %>%
  drop_na(EmployeeNumber) %>%
  distinct(EmployeeID, ClaimCategoryId, DateOccurred, .keep_all = TRUE) %>%
  right_join(driver_info, by = "EmployeeID") %>%
  mutate(driver_age = today() - dmy(BirthDate),
         driver_age = driver_age/dyears(),
         driver_incident = case_when(is.na(ClaimNumber) ~ "No",
                                         !is.na(ClaimNumber) ~ "Yes")) 

inc_severity_age$driver_age <- round(inc_severity_age$driver_age, digits = 0)
inc_severity_age <- inc_severity_age %>%
  mutate(age_group = case_when(driver_age >= 20 & driver_age <= 30 ~ "20-30",
                               driver_age >= 31 & driver_age <= 40 ~ "31-40",
                               driver_age >= 41 & driver_age <= 50 ~ "41-50",
                               driver_age >= 51 & driver_age <= 60 ~ "51-60",
                               driver_age >= 61 & driver_age <= 70 ~ "61-70",
                               driver_age >= 71 & driver_age <= 80 ~ "71-80",
                               driver_age >= 81 & driver_age <= 90 ~ "81-90"))

inc_severity_age <- inc_severity_age %>%
  group_by(age_group, driver_incident, EmployeeID, severity) %>%
  summarise(driver_age_group = n_distinct(EmployeeID)) %>%
  filter(driver_incident == "Yes") %>%
  group_by(age_group, severity) %>%
  summarise(num_drv_inc = sum(driver_age_group))
  
drvr_info_age <- driver_info %>%
  mutate(driver_age = today() - dmy(BirthDate),
         driver_age = driver_age/dyears())
drvr_info_age$driver_age <- round(drvr_info_age$driver_age, digits = 0)
drvr_info_age <- drvr_info_age %>%
  mutate(age_group = case_when(driver_age >= 20 & driver_age <= 30 ~ "20-30",
                               driver_age >= 31 & driver_age <= 40 ~ "31-40",
                               driver_age >= 41 & driver_age <= 50 ~ "41-50",
                               driver_age >= 51 & driver_age <= 60 ~ "51-60",
                               driver_age >= 61 & driver_age <= 70 ~ "61-70",
                               driver_age >= 71 & driver_age <= 80 ~ "71-80",
                               driver_age >= 81 & driver_age <= 90 ~ "81-90"))
drvr_info_age <- drvr_info_age %>%
  group_by(age_group) %>%
  summarise(num_of_drvr = n())

svr_age <- inc_severity_age %>%
  full_join(drvr_info_age, by = "age_group") %>%
  mutate(has_incident_age = (num_drv_inc/num_of_drvr)*100) %>%
  mutate(across(has_incident_age, round, 2)) %>%
  pivot_wider(names_from = severity, values_from = has_incident_age) %>%
  mutate(serious = replace_na(serious, 0),
         slight = replace_na(slight, 0))

p3 <- plot_ly(svr_age, x = ~age_group, mode='markers') %>%
  add_trace(y = ~serious, name = 'serious', type='bar', mode='markers') %>%
  add_trace(y = ~slight, name = 'slight', type='bar', mode='markers') %>%
  layout(
    title = "Proportion of drivers had claims by Age group and Severity",
    xaxis = list(title = "Age group"),
    yaxis = list(title = "Drivers had claims (%)",
                 range=c(0,100)),
    updatemenus = list(
      list(
        type = "buttons",
        label = 'Category',
        buttons = list(
          list(method = "restyle",
               args = list('visible', c(TRUE, FALSE, FALSE)),
               label = "Serious Only"),
          list(method = "restyle",
               args = list('visible', c(FALSE, TRUE, FALSE)),
               label = "Slight Only"),
          list(method = "restyle",
               args = list("visible", TRUE),
               label = "Show All")
        )
      )
    )
  )

htmlwidgets::saveWidget(p3,paste0("p3.html"))
```

<iframe src="p3.html" width="80%" height="380" id="igraph" scrolling="no" seamless="seamless" frameBorder="0"> </iframe>

---

## Age vs MVA Incident ANOVA Test

```{r echo=FALSE, message=FALSE}
age_mva_inc <- incidents %>%
  filter(str_starts(TypeOfClaimName, "MVA")) %>%
  drop_na(EmployeeNumber) %>%
  distinct(EmployeeID, ClaimCategoryId, DateOccurred, .keep_all = TRUE) %>%
  right_join(driver_info, by = "EmployeeID") %>%
  mutate(driver_age = today() - dmy(BirthDate),
         driver_age = driver_age/dyears(),
         driver_incident = case_when(is.na(ClaimNumber) ~ "No",
                                         !is.na(ClaimNumber) ~ "Yes"))
age_mva_inc$driver_age <- round(age_mva_inc$driver_age, digits = 0)
age_mva_inc <- age_mva_inc %>%
  mutate(age_group = case_when(driver_age >= 20 & driver_age <= 30 ~ "20-30",
                               driver_age >= 31 & driver_age <= 40 ~ "31-40",
                               driver_age >= 41 & driver_age <= 50 ~ "41-50",
                               driver_age >= 51 & driver_age <= 60 ~ "51-60",
                               driver_age >= 61 & driver_age <= 70 ~ "61-70",
                               driver_age >= 71 & driver_age <= 80 ~ "71-80",
                               driver_age >= 81 & driver_age <= 90 ~ "81-90")) %>%
  group_by(age_group, driver_incident, EmployeeID) %>%
  summarise(driver_age_group = n_distinct(EmployeeID)) %>%
  group_by(age_group, driver_incident) %>%
  summarise(num_drvage_inc = sum(driver_age_group))

tot_drv_age <- driver_info %>%
  mutate(driver_age = today() - dmy(BirthDate),
         driver_age = driver_age/dyears())

tot_drv_age$driver_age <- round(tot_drv_age$driver_age, digits = 0)

tot_drv_age <- tot_drv_age %>%
  mutate(age_group = case_when(driver_age >= 20 & driver_age <= 30 ~ "20-30",
                               driver_age >= 31 & driver_age <= 40 ~ "31-40",
                               driver_age >= 41 & driver_age <= 50 ~ "41-50",
                               driver_age >= 51 & driver_age <= 60 ~ "51-60",
                               driver_age >= 61 & driver_age <= 70 ~ "61-70",
                               driver_age >= 71 & driver_age <= 80 ~ "71-80",
                               driver_age >= 81 & driver_age <= 90 ~ "81-90")) %>%
  distinct(EmployeeID, age_group) %>%
  group_by(age_group) %>%
  summarise(num_of_drvr = n())

age_inc_tab <- age_mva_inc %>%
  pivot_wider(names_from = driver_incident, values_from = num_drvage_inc) %>%
  left_join(tot_drv_age, by = "age_group") %>%
  mutate(has_incident_age = (Yes/num_of_drvr)*100) %>%
  mutate(across(has_incident_age, round, 2)) %>%
  rename(`age group` = age_group, incident = Yes, `no incident` = No, total = num_of_drvr, prop = has_incident_age) 

# ordinal e.g. 20-30, 41-50, 51-60, 61-70. Same contingency format
age_inc_tab %>%
  kable(caption = "Contingency table for age and incident") %>%
  kable_styling()
```

---

## Age vs MVA Incident ANOVA Test

```{r echo=FALSE}
bin_age <- incidents %>%
  filter(str_starts(TypeOfClaimName, "MVA")) %>%
  drop_na(EmployeeNumber) %>%
  distinct(EmployeeID, ClaimCategoryId, DateOccurred, .keep_all = TRUE) %>%
  right_join(driver_info, by = "EmployeeID") %>%
  mutate(driver_age = today() - dmy(BirthDate),
         driver_age = driver_age/dyears(),
         driver_incident = case_when(is.na(ClaimNumber) ~ "No",
                                         !is.na(ClaimNumber) ~ "Yes"),
         driver_age = round(driver_age,digits=0),
         age_group = case_when(driver_age >= 20 & driver_age <= 30 ~ "20-30",
                               driver_age >= 31 & driver_age <= 40 ~ "31-40",
                               driver_age >= 41 & driver_age <= 50 ~ "41-50",
                               driver_age >= 51 & driver_age <= 60 ~ "51-60",
                               driver_age >= 61 & driver_age <= 70 ~ "61-70",
                               driver_age >= 71 & driver_age <= 80 ~ "71-80",
                               driver_age >= 81 & driver_age <= 90 ~ "81-90")) %>%
  mutate(binary_outcome = case_when(
    driver_incident == 'Yes' ~ 1,
    TRUE ~ 0
  ))

model_fit <- glm(binary_outcome ~ age_group, data=bin_age, family = "binomial") #double check this is logistic regression, not linear regression

# find anova function that gives p value breakdown - something like 
```

.scrollable-slide[
```{r}
summary(model_fit) 
```
]

---

## Age (before & after 70) vs MVA Incident T-Test

```{r echo=FALSE, message=FALSE}
age_mva_inc1 <- incidents %>%
  filter(str_starts(TypeOfClaimName, "MVA")) %>%
  drop_na(EmployeeNumber) %>%
  distinct(EmployeeID, ClaimCategoryId, DateOccurred, .keep_all = TRUE) %>%
  right_join(driver_info, by = "EmployeeID") %>%
  mutate(driver_age = today() - dmy(BirthDate),
         driver_age = driver_age/dyears(),
         driver_incident = case_when(is.na(ClaimNumber) ~ "No",
                                         !is.na(ClaimNumber) ~ "Yes"))
age_mva_inc1$driver_age <- round(age_mva_inc1$driver_age, digits = 0)
yo_70_inc <- age_mva_inc1 %>%
  mutate(age_group = case_when(driver_age < 70 ~ "Younger than 70",
                               driver_age >= 70 ~ "Older than 70")) %>%
  group_by(age_group, driver_incident, EmployeeID) %>%
  summarise(driver_age_group = n_distinct(EmployeeID)) %>%
  group_by(age_group, driver_incident) %>%
  summarise(num_drvage_inc = sum(driver_age_group))

tot_drv_age1 <- driver_info %>%
  mutate(driver_age = today() - dmy(BirthDate),
         driver_age = driver_age/dyears())

tot_drv_age1$driver_age <- round(tot_drv_age1$driver_age, digits = 0)

tot_drv_age1 <- tot_drv_age1 %>%
  mutate(age_group = case_when(driver_age < 70 ~ "Younger than 70",
                               driver_age >= 70 ~ "Older than 70")) %>%
  distinct(EmployeeID, age_group) %>%
  group_by(age_group) %>%
  summarise(num_of_drvr = n())

yo70_inc_tab <- yo_70_inc %>%
  pivot_wider(names_from = driver_incident, values_from = num_drvage_inc) %>%
  left_join(tot_drv_age1, by = "age_group") %>%
  mutate(has_incident_age = (Yes/num_of_drvr)*100) %>%
  mutate(across(has_incident_age, round, 2)) %>%
  rename(`age group` = age_group, incident = Yes, `no incident` = No, total = num_of_drvr, prop = has_incident_age) 


yo70_inc_tab %>%
  kable(caption = "Contingency table for age (before & after 70) and incident") %>%
  kable_styling()
```

```{r echo=FALSE}
test_x2 <- as.matrix(yo70_inc_tab %>%
                      ungroup() %>%
                      select(incident, `no incident`))
CLTest_yo70 <- prop.test(test_x2)
tidy(CLTest_yo70) %>%
  kable() %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "scale_down") %>%
  scroll_box(width = "737px")
```


---

class: middle, center

.full-width[.content-box-duke-green[2) On what day have most incidents been found? Which hours are the peak and trough?]]

---

## Most claims on Tuesdays, least on Sundays

```{r echo=FALSE, fig.dim=c(12,8)}
incidents %>%
  drop_na(EmployeeNumber) %>%
  distinct(EmployeeID, ClaimCategoryId, DateOccurred, .keep_all = TRUE) %>%
  mutate(day_week = weekdays(as.Date(DateOccurred))) %>%
  group_by(day_week) %>%
  summarise(total_cases = n()) %>%
  ggplot(aes(x = factor(day_week, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")), total_cases)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  geom_text(aes(label=total_cases), vjust=1.6, color="white", size=3.5)+
    theme_minimal() +
  labs(y = "Total claim number", x = "Day", title = "Total claim by day of the week")
```

---

## Most claims at peak hours for weekdays, at 3-4pm for weekends

```{r echo=FALSE, message=FALSE, fig.dim=c(12,8)}
incidents %>%
  drop_na(EmployeeNumber) %>%
  distinct(EmployeeID, ClaimCategoryId, DateOccurred, .keep_all = TRUE) %>%
  mutate(day_week = weekdays(DateOccurred),
         hour = hour(DateOccurred)) %>%
  group_by(day_week, hour) %>%
  summarise(total_cases = n()) %>%
  ggplot(aes(x = hour, y = total_cases)) +
  geom_line() +
  facet_wrap(~factor(day_week, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))) +
    theme_minimal() +
  labs(y = "Total claim number", x = "Hour", title = "Total claim by daily hours")

```

---

class: middle, center

.full-width[.content-box-duke-green[3) Is it more dangerous for the bus to travel at night or during the daytime?]]

---

## 5 times more claims made during daytime

```{r echo=FALSE, fig.dim=c(12,8)}
daynight_incidents <- incidents %>%
  drop_na(EmployeeNumber) %>%
  distinct(EmployeeID, ClaimCategoryId, DateOccurred, .keep_all = TRUE) %>%
  mutate(hour = hour(DateOccurred))

daynight_incidents %>%
  mutate(day_night = case_when(hour >= 19 | hour %in% c(0, 1, 2, 3, 4) ~ "night",
                               hour < 19 ~ "day")) %>%
  group_by(day_night) %>%
  summarise(total_cases = n()) %>%
  ggplot(aes(x = day_night, y = total_cases, fill = day_night)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=total_cases), vjust=1.6, color="white", size=3.5) +
  theme_minimal() +
  theme(legend.position = "none") +
  labs(x = "Daytime/night", y = "Total claim number", title = "Total claims made during daytime and night")
```

---

class: middle, center

.full-width[.content-box-duke-green[4) What kind of weather (temperature and precipitation) is considered safer or dangerous for bus drivers?]]

---

## Most incidents found with rainfall from 1.5 to 4.5 (mm)

```{r echo=FALSE, fig.dim=c(12,8)}
dh_mva_incidents <- incidents %>%
  drop_na(EmployeeNumber) %>%
  distinct(EmployeeID, ClaimCategoryId, DateOccurred, .keep_all = TRUE) %>%
  mutate(date_hour = format(DateOccurred, format = "%Y-%m-%d %H")) %>%
  filter(company %in% c("TDNSW", "TDM"),
         str_starts(TypeOfClaimName, "MVA"))

melbourneweather <- melbourneweather %>%
  mutate(company = "TDM",
         date_hour = format(timestamp, format = "%Y-%m-%d %H")) %>%
  rename(Temperature = `Melbourne Temperature`, Precipitation = `Melbourne Precipitation Total`)

sydneyweather <- sydneyweather %>%
  mutate(company = "TDNSW",
         date_hour = format(timestamp, format = "%Y-%m-%d %H")) %>%
  rename(Temperature = `Sydney Temperature`, Precipitation = `Sydney Precipitation Total`)

mel_syd_weather <- rbind(melbourneweather, sydneyweather)

weather_n_incidents <- mel_syd_weather %>%
  mutate(hour = hour(timestamp)) %>%
  left_join(dh_mva_incidents, by = c("company", "date_hour")) %>%
  mutate(Temperature = as.numeric(Temperature),
         Precipitation = as.numeric(Precipitation),
         rain = case_when(Precipitation >= 2.5 ~ "Yes",
                          Precipitation < 2.5 ~ "No"),
         has_incident = case_when(is.na(ClaimNumber) ~ "No",
                                         !is.na(ClaimNumber) ~ "Yes"))

weather_n_incidents %>%
  filter(rain == "Yes") %>%
  ggplot(aes(x = Precipitation, group = has_incident, fill = has_incident)) +
  geom_density(alpha = 0.5) +
  facet_wrap(~company, nrow = 2) +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  scale_fill_discrete(labels=c("Non-incident", "Incident")) +
  labs(x = "Rainfall (mm)", title = "Incident and non-incident distribution under rainy condition measured by precipitation") +
  expand_limits(x = -0.5)


```

---

## Most incidents found with rainfall close to 0

```{r echo=FALSE, fig.dim=c(12,8)}
weather_n_incidents %>%
  filter(rain == "No") %>%
  ggplot(aes(x = Precipitation, group = has_incident, fill = has_incident)) +
  geom_density(alpha = 0.5) +
  facet_wrap(~company, nrow = 2) +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  scale_fill_discrete(labels=c("Non-incident", "Incident")) +
  labs(x = "Rainfall (mm)", title = "Incident and non-incident distribution under little/no rain condition measured by precipitation") +
  expand_limits(x = -0.2:2.4)


```

---

## log scale distribution under little/no rain and rainy condition (not normally distributed)

```{r message=FALSE, include=FALSE}
# compare precipitation between has_incident=yes and has_incident=no
rain_inc <- weather_n_incidents %>%
  select(Precipitation, has_incident) 
```

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.dim=c(12,8)}
ggplot(rain_inc, aes(Precipitation)) +
        geom_histogram(fill = "white", color = "grey30") +
        facet_wrap(~has_incident) +
        scale_x_log10() +
  labs(title = "Log incidents under little to no rain and rainy condition")
```

---

## Rain condition vs incidents Wilcox test 

```{r message=FALSE}
wilcox.test(Precipitation ~ has_incident, data = rain_inc)
# is associated, relationship
```

---

## Most incidents found with moderate temperature

```{r echo=FALSE, fig.dim=c(12,8)}
weather_n_incidents %>%
  ggplot(aes(x = Temperature, group = has_incident, fill = has_incident)) +
  geom_density(alpha = 0.5) +
  facet_grid(~company) +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  scale_fill_discrete(labels=c("Non-incident", "Incident")) +
  labs(x = "Temperature (°C)", title = "Incident and non-incident distribution measured by temperature")

```

---

# Temperature vs incidents distribution (normally distributed)

```{r include=FALSE}
temp_inc <- weather_n_incidents %>%
  select(Temperature, has_incident) 
```

```{r echo=FALSE, message=FALSE, fig.dim=c(12,8)}
ggplot(temp_inc, aes(Temperature)) +
        geom_histogram(fill = "white", color = "grey30") +
        facet_wrap(~has_incident) 
```

---

## Temperature vs Incidents T-Test

```{r echo=FALSE, message=FALSE}
t.test(Temperature ~ has_incident, data = temp_inc)
# the existence of significance difference
```

---

class: middle, center

.full-width[.content-box-duke-green[5) Is there a relationship between drivers' driving hours within a day and the likelihood of getting into an incident?]]


---

## Distribution of incidents & Hour of driving classfied by day & night

```{r echo=FALSE, fig.dim=c(12,8)} 
tmp2_when_occur <- tmp2 %>%
  filter(match_type == 2) %>%
  distinct(EmployeeID, ClaimCategoryName, DateOccurred, .keep_all = TRUE) %>%
  mutate(diff_occur_start = difftime(DateOccurred, shift_start),
         diff_occur_start = diff_occur_start/dhours(),
         hour = hour(DateOccurred),
         day_night = case_when(hour >= 19 | hour %in% c(0, 1, 2, 3, 4) ~ "Night",
                               hour < 19 ~ "Day")) %>%
  filter(str_starts(TypeOfClaimName, "MVA"))
tmp2_when_occur$diff_occur_start <- round(tmp2_when_occur$diff_occur_start, digits = 0) 

ggplot(tmp2_when_occur, aes(x = diff_occur_start)) +
  geom_histogram(aes(y = ..density..), bins = 25, alpha = 0.4) +
  geom_density() +
  facet_grid(~day_night) +
  theme_minimal() +
  labs(x = "Number of hour(s) after shift start", title = "Hour(s) that claims made after drivers' driving hours in NSW")

```

---

## Random Forest

```{r echo=FALSE, message=FALSE}
# fix the original random forest dataframe
nswshifts1 <- nswshifts %>%
  rename(shift_start = VdsTripStartTime, shift_end = VdsTripEndTime) %>%
  mutate(JoinDate = as.Date(shift_start)) %>%
  select(EmployeeID, shift_start, shift_end, JoinDate)

incident1 <- incidents %>%
  drop_na(EmployeeNumber) %>%
  distinct(EmployeeID, ClaimCategoryId, DateOccurred, .keep_all = TRUE) %>%
  filter(company == "TDNSW", str_starts(TypeOfClaimName, "MVA")) %>%
  mutate(JoinDate = as.Date(DateOccurred)) %>%
  group_by(EmployeeID, JoinDate) %>%
  select(EmployeeID, DateOccurred, JoinDate)

nswshifts_lj_inc <- nswshifts1 %>%
  group_by(EmployeeID, JoinDate) %>%
  summarise(shift_start = min(shift_start)-30*60,
            shift_end = max(shift_end)+30*60) %>%
  left_join(incident1, by = c("EmployeeID", "JoinDate")) %>%
  select(EmployeeID, shift_start, shift_end, DateOccurred) %>%
  mutate(has_incident = case_when(is.na(DateOccurred) ~ "No",
                                         !is.na(DateOccurred) ~ "Yes"))

long_shifts_inc <- nswshifts_lj_inc %>%
  mutate(shift_date = as.Date(shift_start),
         shift_start_hour = hour(shift_start),
         shift_end_hour = hour(shift_end),
         Occurred_hour = hour(DateOccurred)) %>% 
  mutate(shift_end_hour = case_when(shift_end_hour < shift_start_hour ~ 24+shift_end_hour,
                                    TRUE ~ as.numeric(shift_end_hour)),
         trip_duration = difftime(shift_end, shift_start),
         trip_duration = trip_duration/dhours()) %>%
  filter(trip_duration < 24,
         shift_start_hour < 22, shift_start_hour > 4) %>%
  # creating list of shift hours between start and end hour & then unnesting the dataframe to make it long
  rowwise() %>%
  mutate(shift_hour_of_day = list(c(shift_start_hour:shift_end_hour))) %>%
  unnest(cols = c(shift_hour_of_day)) %>%
  mutate(shift_hour_for_driver = shift_hour_of_day - shift_start_hour) %>%
  # some further wrangling to remove unneccessary columns & convert incident hour into hourly indicator & restrict inc
  mutate(incident_indicator = case_when(
    Occurred_hour == shift_hour_of_day ~ 1,
    TRUE                               ~ 0
  )) %>%
  select(-shift_start, -shift_end, -DateOccurred, -Occurred_hour) 

sydneyweather_dh <- sydneyweather %>%
  mutate(date = as.Date(timestamp),
         hour = hour(timestamp),
         hour = case_when(hour == 0 ~ 24,
                          TRUE ~ as.numeric(hour)))

nsw_fit_df <- long_shifts_inc %>%
  left_join(sydneyweather_dh, by = c("shift_date" = "date", "shift_hour_of_day" = "hour")) %>%
  left_join(driver_info, by = "EmployeeID") %>%
  ungroup() %>%
  select(-EmployeeID, -has_incident, -shift_date, -shift_start_hour, -shift_end_hour, -trip_duration, -timestamp, -Depot, -CompanyID, -EmployeeStartDate, -EmploymentTerminationDate, -Position, -ContractType, -FTE, -BirthDate, -company, -date_hour) 
  
```

```{r echo=FALSE}
set.seed(2021)

nsw_fit_df <- nsw_fit_df %>%
  na.omit() %>%
  mutate(incident_indicator = factor(incident_indicator)) 
nsw_fit_split <- initial_split(nsw_fit_df, 2/3,
                                         strata = incident_indicator)
nsw_fit_tr <- training(nsw_fit_split) %>% 
  mutate(Gender = factor(Gender)) %>% 
  mutate(Precipitation = as.numeric(Precipitation)) %>%
  mutate(Temperature = as.numeric(Temperature))
nsw_fit_ts <- testing(nsw_fit_split)

up_train <- upSample(x = nsw_fit_tr[, -ncol(nsw_fit_tr)],
                     y = nsw_fit_tr$incident_indicator)                         
table(up_train$Class) 


nsw_fit_rf <- randomForest(incident_indicator ~ shift_hour_of_day+shift_hour_for_driver+Temperature+Precipitation, data = up_train, importance = TRUE)
print(nsw_fit_rf)

```

---

## Variables importance

```{r echo=FALSE}
importance(nsw_fit_rf)
varImpPlot(nsw_fit_rf)
```

---

```{r echo=FALSE, fig.dim=c(12,8)}
plot_predict_interaction(nsw_fit_rf, up_train, "shift_hour_of_day", "shift_hour_for_driver")
```

---

```{r echo=FALSE, fig.dim=c(12,8)}
plot_predict_interaction(nsw_fit_rf, up_train, "Temperature", "Precipitation")
```

---

class: middle

# References:

.tiny[
Alboukadel Kassambara (2021). rstatix: Pipe-Friendly Framework for Basic Statistical Tests.
  R package version 0.7.0. https://CRAN.R-project.org/package=rstatix

Aleksandra Paluszynska, Przemyslaw Biecek and Yue Jiang (2020). randomForestExplainer:
  Explaining and Visualizing Random Forests in Terms of Variable Importance. R package version
  0.10.1. https://CRAN.R-project.org/package=randomForestExplainer

A. Liaw and M. Wiener (2002). Classification and Regression by randomForest. R News 2(3),
  18--22.

Bob Rudis (2020). hrbrthemes: Additional Themes, Theme Components and Utilities for
  'ggplot2'. R package version 0.8.0. https://CRAN.R-project.org/package=hrbrthemes

Claus O. Wilke (2021). ggridges: Ridgeline Plots in 'ggplot2'. R package version 0.5.3.
  https://CRAN.R-project.org/package=ggridges
  
C. Sievert. Interactive Web-Based Data Visualization with R, plotly, and shiny. Chapman and
  Hall/CRC Florida, 2020.

David Robinson, Alex Hayes and Simon Couch (2021). broom: Convert Statistical Objects into
  Tidy Tibbles. R package version 0.7.5. https://CRAN.R-project.org/package=broom

Garrett Grolemund, Hadley Wickham (2011). Dates and Times Made Easy with lubridate. Journal
  of Statistical Software, 40(3), 1-25. URL https://www.jstatsoft.org/v40/i03/.

Hao Zhu (2021). kableExtra: Construct Complex Table with 'kable' and Pipe Syntax. R package
  version 1.3.4. https://CRAN.R-project.org/package=kableExtra

Julia Silge, Fanny Chow, Max Kuhn and Hadley Wickham (2021). rsample: General Resampling
  Infrastructure. R package version 0.0.9. https://CRAN.R-project.org/package=rsample

Max Kuhn and Davis Vaughan (2021). parsnip: A Common API to Modeling and Analysis Functions.
  R package version 0.1.5. https://CRAN.R-project.org/package=parsnip

Max Kuhn (2020). caret: Classification and Regression Training. R package version 6.0-86.
  https://CRAN.R-project.org/package=caret

R Core Team (2021). R: A language and environment for statistical computing. R Foundation
  for Statistical Computing, Vienna, Austria. URL https://www.R-project.org/.
  
Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43),
  1686, https://doi.org/10.21105/joss.01686

]

---

class: inverse, center, middle
# Thank you! 


<span class="cc">
<!-- Key: a: SA, b: BY, c: CC Circle, d: ND, n: NC, m: Sampling, s: Share, r: Remix, C: CC Full Logo -->
</span>


[CC BY-NC license](https://creativecommons.org/licenses/by-nc/4.0/)


